Ontologien aus dem Bereich der Industrie (TODO)

### 2024-03-05 paper.tex
added basic graphviz config to visualize ontology relations

>>>>

\subsubsection{DCElements + DCTerms}

TODO:

@prefix dcat: <http://www.w3.org/ns/dcat#> .
@prefix dcmitype: <http://purl.org/dc/dcmitype/> .
@prefix dcterms: <http://purl.org/dc/terms/> .
@prefix foaf: <http://xmlns.com/foaf/0.1/> .
@prefix owl: <http://www.w3.org/2002/07/owl#> .
@prefix rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#> .
@prefix rdfs: <http://www.w3.org/2000/01/rdf-schema#> .
@prefix schema: <https://schema.org/> .
@prefix skos: <http://www.w3.org/2004/02/skos/core#> .
@prefix void: <http://rdfs.org/ns/void#> .
